Unity in diversity: Children from 17 diverse communities process gaze in similar ways

### 2024-03-15 paper/supplement.Rmd
add missing site descriptions to supplement

Akure is situated in the Ondo State in southwest Nigeria. About 800,000 people live in this medium-sized city, and most of them are from the nearby urban and rural areas.

@@

Akure's natural surroundings are enhanced by the abundant vegetation that includes dense forests, beautiful farmlands, and vivid flora, which is fostered by the climate and fertile soils.

Akure boasts a diverse populace, representing a cultural mosaic where the Yoruba, Igbo, and Hausa communities coexist harmoniously. While the Yoruba ethnicity predominates, English serves as a widely spoken language alongside the native tongue.

@@

Auckland | Tāmaki Makaurau is the largest city of New Zealand | Aotearoa with a population of about 1.5 million people. The city is located on the North Island | Te Ika-a-Māui inbetween the Hauraki Gulf | Tīkapa Moana to the East and the Waitākere Ranges to the West. The climate is defined as either oceanic (Cfb) or subtropical (NIWA). Temperatures are mild throughout the year, with an average temperature of 23.7 during summer and 14.7 during winter months.

@@

Education levels are generally good in Auckland. 18.6% of the population hold a Bachelor's Degree. Interestingly about 9.1% move overseas for their secondary education. Parenting and childcare practises are comparable to other western cultures, with some adjustments being implemented in recent years to include more Māori cultural practises in education programs. Such as starting the day or specific activities | hui with Karakia, a form of incantation to ensure a favorable outcome to important events and undertakings. (see Literature for further information on early childhood education in New Zealand.)

Aotearoa is an industrialized nation, nearly everybody has a smartphone and uses technology in their everyday life. Many administrative processes are very much digitized. There is no perceived mistrust towards technology and new developments are generally embraced with great interest.

@@

### Bandongo (Rep. Congo) - Ethnic group

@@

* ...

### Bayaka (Rep. Congo) - Ethnic group

* ...

@@

Beijing, a municipality directly under the Central Government, is the capital of the People's Republic of China and the country's political, economic, cultural and transportation center as well as a famous historic city and a modern international city. Beijing covers an area of 16,410.54 square kilometers (sq.km) with a population of 21,843,000 in 2022. Beijing ranked second in Chinese cities in terms of GDP in 2022. Geographically, Beijing is located in the northern part of the North China Plain.

Beijing is an inland city and is surrounded by mountains to its west, north and northeast. Mountain areas occupy about 62% of the municipality's total area. The land is characterized by urban and suburban areas, with parks, squares, and historical buildings located mostly in the downtown districts, and flat agricultural land and mountains in the suburban districts. Beijing has a temperate, continental monsoonal climate, characterized by short spring and autumns, hot and rainy summers, and cold and dry winters. Its average annual temperature is 11 to 14oC. The coldest month in Beijing is January, with an average temperature of -9 to -4°C; the hottest month is July, with an average of 25°C. Around 75 percent of its annual precipitation occurs in summer, with the heaviest rainfall in July and August.

According to the 2021 National Census data, in Beijing, there were 20845166 (95%) Han Chinese along with 1047929 (4.8%) people in other minority nationalities (e.g., Manchu, Hui ethnic, Mongolian ethnic). Mandarin Chinese is commonly spoken by all ethnic groups though many of the minority nationalities also have their own national languages, such as Mongolian language used by Mongolian ethnic. (4)

Beijing is one of the birthplaces of Chinese Civilization and one of the five ancient capital cities in China. With but few interruptions, Beijing has been the capital of China for some eight centuries: including the capital of the State of Yan during the Western Zhou Dynasty (11th Century-771BC), the capital of Jin Dynasty (1153-1215), the capital of Yuan Dynasty (1271-1368), the capital of Ming Dynasty (1421-1644), and the capital of Qing Dynasty (1644-1912). In 1949, Beiping (former name of Beijing) was renamed Beijing and became the capital of the People’s Republic of China. Since then, it gradually develops into a modern metropolis.

@@

It’s common that parents spend large parts of the day away from home and children are cared for externally. Between 2 and 3 years of age young children can attend nurseries (very few nurseries accept children as young as 1.5-year-old). Nurseries are largely commercialized and non-subsidized. Starting at age 3, children can attend either publicly subsidized kindergarten or private kindergarten. Children move on to primary school at six. Public primary education is free and compulsory. There are also private primary schools that cater to other groups, such as international primary schools that serve families catering to the expatriate community and families seeking an international education, as well as those who want to get prepared for studying abroad later. The samples of the current study were drawn from public kindergarten and public primary school.

@@

The city has a humid, subtropical climate and has generally mild weather. The average temperatures range from 11 degrees Celsius (July) to 25 degrees (January), but heat waves are common during the summer months (December to February).

@@

Chimfunshi wildlife orphanage is an NGO providing a home for about 150 chimpanzees. The sanctuary is located in the Copperbelt region in the northern part of Zambia close to the DRC border. The chimpanzees are housed in eight different enclosures; each of an area up to 121.5Ha. The Sanctuary provides education, housing and medical care for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.

@@

The Khwe (also referred to as Khoe, Khwedam, or Barakhoena) people reside in their ancestral lands within today’s Bwabwata National Park in northwestern Namibia and the bordering regions in Angola and Botswana. There is also a Khwe community in today’s South Africa that has moved there while Namibia became independent in 1990. The current research was conducted in the Namibian Zambezi region which is home to numerous small Khwe communities. There are an estimated 3,000 to 5,000 Khwe residing in Bwabwata as of today.

@@

Leipzig is a medium-sized city located in the east of Germany with a population of approximately 620,000. It serves as a significant urban center within the state of Saxony. Geographically, Leipzig is situated in the southernmost part of the North German Plain.

@@

Malatya is a big city located in the Eastern Anatolia region of Turkey with a population of approximately 800,000. Due to its strong economy based on agriculture, it is one of the biggest cities in eastern Turkey.

@@

Nyabyeya is located on a green, gently sloping area behind Nyabyeya Hill and is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C/90°F and cooler nights at 17°C/63°F. The region observes two distinct agricultural seasons - a wet season from late March to June and August to November, followed by a dry season from early December to March.

@@

* Budongo Conservation Field Station: http://www.budongo.org/
* Holden, E., Buryn-Weitzel, J. C., Atim, S., Biroch, H., Donnellan, E., Graham, K. E., Hoffman, M., Jurua, M., Knapper, C. V., Lahiff, N. J., Marshall, S., Paricia, J., Tusiime, F., Wilke, C., Majid, A., & Slocombe, K. E. (2022). Maternal attitudes and behaviours differentially shape infant early life experience: A cross cultural study. PLOS ONE, 17(12), e0278378. https://doi.org/10.1371/journal.pone.0278378

@@

Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km2  inside the Mexican State (Ocuilan, n.d.). Geographically Ocuilan has an altitude of between 1000 to 2,600 m situated 80 km south of Mexico City. (INEGI,2010)

@@

Plymouth is a coastal city in the South West of England with a population of more than 260,000 inhabitants. About 91% of the population was born in the UK and of those born outside of the UK, the largest proportion comes from the EU (4.5%). 95% of residents identified as White, 2.3% as Asian, and 1% as Black. English is the predominant language spoken in the city.

The city has a temperate oceanic climate with average temperatures ranging from 4 to 20 degrees Celsius. Winters are generally mild, and temperatures rarely drop below zero degrees. Rain is frequent and highest in autumn and winter.

@@

Pune is located in the state of Maharashtra in western India. The city’s total area is 15.642 square kilometres and the municipal corporation area covers 518 square kilometers. It lies on the western margin of the Deccan plateau at an altitude of 1840 feet. It is on the leeward side of the Sahyadri mountain range which forms a barrier with the Arabian Sea. The population within city limits is 4.5 million while including the metro population, it stands at 7.1 million. Pune is one of the largest information technology hubs in India and is also an important automobile and manufacturing hub. Sixty-two percent of the population in Pune is under the age of 30. The top three industries that offer employment are automotive, manufacturing and information technology and start-ups. Automobile industries such as Tata Motors, Jaguar, Renault, Volkswagen, General motors, Skoda, Force motors, Kinetic motors  and Mercedes-Benz have their manufacturing plants in Chakan, an industrial area around Pune. Cummins, a leading manufacturer of diesel and natural gas engines as well as JCB, the farm equipment company are other renowned investors. The manufacturing industry provides employment to over 600,000 people while the IT sector employs over 350,000 people. About 2.2 million migrant workers are employed in the automobile, construction and medium scale manufacturing industries.

Pune is referred to as the ‘Oxford of the East’ because of its reputed educational institutions and is also considered to be one of the most livable cities in India. The literacy rate in Pune is 86.15%.  As a result of rapid industrialization since the 1960s, a large number of people moved to Pune. Since there was inadequate housing to meet the demand, there was an increase in the number of slum dwellers. Nearly half of the slum dwellers do not have in-house toilets and 10% do not have electricity. 
Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28 degrees Celsius. Summer, monsoon and winter are the three main seasons with May being the hottest month. During summer, i.e. mid-March to mid-June, temperatures can go as high as 42 degrees Celsius. Monsoon lasts from June to October with most of the annual rainfall of 722mm falling between June and September with July being the wettest month. In the months of December and January, temperatures remain around 29 degrees Celsius with overnight temperatures dropping to below 12 degrees.

@@

The city is a large metropolitan area with urban and suburban areas bordered by mountain ranges to the east and west. The land is characterized by bay flats and hills with several rivers running through the city. San Jose’s climate is described as mild, semi-arid, and Mediterranean. A wet season typically occurs between November and March with combined rainfall and an average daytime temperature of 50 degrees Fahrenheit. A dry season occurs between March and November where precipitation is minimal and the average daytime temperature is 70 degrees Fahrenheit.

@@

@@

* ...

>>>>

Akure is situated in the Ondo State in southwest Nigeria. About 800,000 people live in this medium-sized city. Most inhabitants moved from the nearby urban and rural areas to Akure.

@@

Akure's natural surroundings are enhanced by the abundant vegetation that includes dense forests, farmlands, and vivid flora, which is fostered by the climate and fertile soils.

Akure boasts a diverse populace, representing a cultural mosaic where the Yoruba, Igbo, and Hausa communities coexist. While the Yoruba ethnicity predominates, English serves as a widely spoken language alongside the native tongue.

@@

Auckland | Tāmaki Makaurau is the largest city of New Zealand | Aotearoa with a population of about 1.5 million people. The city is located on the North Island | Te Ika-a-Māui inbetween the Hauraki Gulf | Tīkapa Moana to the East and the Waitākere Ranges to the West. The climate is defined as either oceanic (Cfb) or subtropical (NIWA). Temperatures are mild throughout the year, with an average temperature of 23.7°C during summer and 14.7°C during winter months.

@@

Education levels are generally high in Auckland. 18.6% of the population hold a Bachelor's degree. Interestingly, about 9.1% move overseas for their secondary education. Parenting and childcare practices are comparable to other western cultures, with some adjustments being implemented in recent years to include more Māori cultural practices in education programs. Such as starting the day or specific activities | hui with Karakia, a form of incantation to ensure a favorable outcome to important events and undertakings. (see Literature for further information on early childhood education in New Zealand.)

Aotearoa is an industrialized nation, nearly everybody has a smartphone and uses technology in their everyday life. Many administrative processes are digitized. There is no perceived mistrust towards technology and new developments are generally embraced with great interest.

@@

### Bandongo and BaYaka (Rep. Congo) - Ethnic groups

Both BaYaka and Bandongo populations live (seasonally) in a remote village located in the Likouala region of the Republic of the Congo. The Republic of the Congo is located in the central-western part of sub-Saharan Africa along the equator. The Likouala department is located in the country's north, in the Congo River Basin, bordering the Central African Republic and the Democratic Republic of Congo.
The region's climate is tropical, with temperatures ranging from 34°C to 23°C yearly and 148.73 mm of rainfall yearly (Weather and Climate, 2024). The dry season starts from December until March, with a mild, rainy season from April until August. Heavier rains happen between September and November.

The village is inhabited by approximately 300 BaYaka and 300 Bandongo people (estimates from 2019). The BaYaka and Bandongo people have co-inhabited the rainforests of the Congo basin for approximately 3.000 years (Takeuchi, 2014) and have developed inter-ethnic kin (or patronage) and commercial relationships with one another (Lewis, 2002). Despite this historical coexistence, each cultural group has distinct means of subsistence and speaks their own language; for the Bandongo, this is Bondongo (Bantu C142); for the BaYaka, this is Yaka (C104); although Lingala (Bantu C36d) is often used as lingua-franca between groups) (Hammarström, 2019). The BaYaka are one of many hunter-gatherer societies living in the Congo Basin (Bahuchet, 2017). Like many other hunter-gatherer groups in the world, the BaYaka are egalitarian (Boyette & Hewlett, 2017; Woodburn, 1982), follow an autonomy foundational schema (Boyette & Hewlett, 2017), share resources and parental care (Lewis, 2016) and are characterized by an immediate-return economy with an absence of food storage techniques (Lewis, 2002). The BaYaka forage for food items in the forests they inhabit while supplementing their diets with some agricultural items (Boyette et al., 2020; Kitanishi, 1995). The Bandongo mainly rely on fishing and agriculture to obtain their nutrition (Komatsu, 1998). Although the Bandongo also practice hunting to some extent, it is mainly directed to smaller game species, often sourced with the intent to sell, while BaYaka focus on a wider range of species and bigger game for subsistence (Fa et al., 2016). BaYaka and Bandongo groups sometimes collaborate in their subsistence activities, such as hunting and fishing (Jang & Boyette, 2021; Kandza et al., 2023). Contrary to BaYaka, Bandongo live in a stratified and hierarchical society characterized by wealth accumulation and authority (Boyette et al., 2018).

In the forest camps, the BaYaka inhabit temporary houses (called mongulo or ekuta, depending on the region) built with Marantaceae leaves, lianas, palm tree leaves, etc. (see Lewis, 2002). These structures are occupied by several family members (usually, but not always, grandparents, parents, and their children). Older children may sometimes build their own ekuta, where they sleep alone or with other children. The area of forest camps varies, but usually they are small, leading to ekutas being built relatively close to each other (Lew-Levy et al., 2020). In the village, BaYaka tend to live in unoccupied Bandongo houses or build their own houses with branches and adobe. Bandongo families build permanent habitation with very clear delimitations, usually consisting of a house where the family lives and a kitchen, both built with adobe and thatch roofs (Boyette et al., 2018). Households in the village are usually organized based on patrilineal families.

In BaYaka and Bandongo communities, children acquire information through teaching and observational learning from adults and other children (Boyette & Hewlett, 2017; Lew-Levy et al., 2020). However, the types of teaching may differ between the two groups. Due to their focus on individual autonomy, BaYaka has been reported to show lower levels of direct instruction compared to farmer groups (Boyette & Hewlett, 2017).  Both communities show alloparental care for children, but while BaYaka caregiving encompasses members of both sexes and different ages within the community, Bandongo alloparenting is provided mainly by women belonging to the extended family of the children (Boyette et al., 2018, 2020).

BaYaka children have limited to no exposure to formal education, and the same is true for most BaYaka parents. Bandongo children often attend primary school in the village. Some of those children choose to continue into higher levels of education, usually up to high school, in nearby towns. It is likely that the parents of the children tested completed at least primary school, but we did not directly ask them in this study.

In the village where this research was conducted, BaYaka and Bandongo people have limited access to market goods or electronic technology. BaYaka, in particular, may only have access to the goods brought by the market boat every two weeks (e.g., radios, flip-flops, machetes, torches) or those available through commercial exchange with their Bandongo neighbors. However, the Bandongo often have more access to commercial items when visiting nearby towns. Although exposure to display screens is rare, the research team found a television used communally by the village people in 2023 (time of data collection). A smaller television was found in a BaYaka camp in 2022 (the television belonged to a Bandongo man). No touchscreen device has been observed to be used by either community outside of a research setting.

Children from both communities were recruited after their parents or guardians provided explicit informed consent. The experiment was conducted in the research house, which has a central location in the village. Before experimentation, children’s consent was requested, at which point, children were free to opt out of participating. Children were paired with a same-cultural group experimenter. Children had the experiment presented in their primary spoken languages; for BaYaka, this was Yaka, and for Bandongo, this was Lingala. Children received pre-recorded instructions from the testing computer, as well as some additional instructions, reiterating the recordings when needed.

@@

* Bahuchet, S. (2017). Cultural diversity of African pygmies. In Hunter-gatherers of the Congo Basin (pp. 1-30). Routledge.
Boyette, A. H., & Hewlett, B. S. (2017). Autonomy, Equality, and Teaching among Aka Foragers and Ngandu Farmers of the Congo Basin. Human Nature, 28(3), 289–322. https://doi.org/10.1007/s12110-017-9294-y
* Boyette, A. H., Lew-Levy, S., & Gettler, L. T. (2018). Dimensions of Fatherhood in a Congo Basin Village: A Multimethod Analysis of Intracultural Variation in Men’s Parenting and Its Relevance for Child Health. Current Anthropology, 59(6), 839–847. https://doi.org/10.1086/700717
* Boyette, A. H., Lew‐Levy, S., Sarma, M. S., Valchy, M., & Gettler, L. T. (2020). Fatherhood, egalitarianism, and child health in two small‐scale societies in the Republic of the Congo. American Journal of Human Biology, 32(4). https://doi.org/10.1002/ajhb.23342
* Fa, J. E., Olivero, J., Farfán, M. A., Lewis, J., Yasuoka, H., Noss, A., Hattori, S., Hirai, M., Kamgaing, T. O. W., Carpaneto, G., Germi, F., Márquez, A. L., Duarte, J., Duda, R., Gallois, S., Riddell, M., & Nasi, R. (2016). Differences between Pygmy and Non-Pygmy Hunting in Congo Basin Forests. PLOS ONE, 11(9), e0161703. https://doi.org/10.1371/journal.pone.0161703
* Hammarström, H. (2019). An inventory of Bantu languages. In The Bantu languages (pp. 17-78). Routledge.
* Jang, H., & Boyette, A. H. (2021). Observations of Cooperative Pond Fishing by the Bayaka and Bantu People in the Flooded Forest of the Northern Republic of Congo (2). The Center for African Area Studies, Kyoto University. https://doi.org/10.34548/asm.41.2.1
* Kandza, V. H., Jang, H., Ntamboudila, F. K., Lew-Levy, S., & Boyette, A. H. (2023). Intergroup Cooperation in Shotgun Hunting Among BaYaka Foragers and Yambe Farmers from the Republic of the Congo. Human Nature, 34(2), 153–176. https://doi.org/10.1007/s12110-023-09448-0
* Kitanishi, K. (1995). Seasonal Changes in the Subsistence Activities and Food Intake of the Aka Hunter-Gatherers in Northeastern Congo (2). The Center for African Area Studies, Kyoto University. https://doi.org/10.14989/68133
* Lewis, J. (2002). Forest hunter-gatherers and their world: A study of the Mbendjele Yaka pygmies of Congo-Brazzaville and their secular and religious activities and representations (Doctoral dissertation, University of London).
* Lewis, J. (2016). Play, music, and taboo in the reproduction of an egalitarian society. Social learning and innovation in contemporary hunter-gatherers: Evolutionary and ethnographic perspectives, 147-158.
* Lew-Levy, S., Kissler, S. M., Boyette, A. H., Crittenden, A. N., Mabulla, I. A., & Hewlett, B. S. (2020). Who teaches children to forage? Exploring the primacy of child-to-child teaching among Hadza and BaYaka Hunter-Gatherers of Tanzania and Congo. Evolution and Human Behavior, 41(1), 12–22. https://doi.org/10.1016/j.evolhumbehav.2019.07.003
* Takeuchi, K. (2014). In: Barry S. Hewlett ed. Hunter-Gatherers of the Congo Basin: Cultures, Histories and Biology of Arican Pygmies, 2014. Transaction Publishers, New Brunswick.
* Weather and Climate. (2024). Https://weatherandclimate.com/republic-of-the-congo/likouala/impfondo.
* Woodburn, J. (1982). Egalitarian Societies. Man, 17(3), 431. https://doi.org/10.2307/2801707

@@

Beijing, a municipality directly under the Central Government, is the capital of the People's Republic of China and the country's political, economic, cultural and transportation center as well as a famous historic city and a modern international city. Beijing covers an area of 16 410 54 km^2^ with a population of 21 843 000 in 2022. Beijing ranked second in Chinese cities in terms of GDP in 2022. Geographically, Beijing is located in the northern part of the North China Plain.

Beijing is an inland city and is surrounded by mountains to its west, north and northeast. Mountain areas occupy about 62% of the municipality's total area. The land is characterized by urban and suburban areas, with parks, squares, and historical buildings located mostly in the downtown districts, and flat agricultural land and mountains in the suburban districts. Beijing has a temperate, continental monsoonal climate, characterized by short spring and autumns, hot and rainy summers, and cold and dry winters. Its average annual temperature is 11 to 14°C. The coldest month in Beijing is January, with an average temperature of -9 to -4°C; the hottest month is July, with an average of 25°C. Around 75 percent of its annual precipitation occurs in summer, with the heaviest rainfall in July and August.

According to the 2021 National Census data, in Beijing, there were 20 845 166 (95%) Han Chinese along with 1 047 929 (4.8%) people in other minority nationalities (e.g., Manchu, Hui ethnic, Mongolian ethnic). Mandarin Chinese is commonly spoken by all ethnic groups though many of the minority nationalities also have their own national languages, such as Mongolian language used by Mongolian ethnic. (4)

Beijing is one of the birthplaces of Chinese Civilization and one of the five ancient capital cities in China. With but few interruptions, Beijing has been the capital of China for some eight centuries: including the capital of the State of Yan during the Western Zhou Dynasty (11th Century - 771 BCE), the capital of Jin Dynasty (1153 - 1215), the capital of Yuan Dynasty (1271 - 1368), the capital of Ming Dynasty (1421-1644), and the capital of Qing Dynasty (1644 - 1912). In 1949, Beiping (former name of Beijing) was renamed Beijing and became the capital of the People’s Republic of China. Since then, it gradually develops into a modern metropolis.

@@

It’s common that parents spend large parts of the day away from home and children are cared for externally. Between 2 and 3 years of age young children can attend nurseries (very few nurseries accept children as young as 1.5 years old). Nurseries are largely commercialized and non-subsidized. Starting at age 3, children can attend either publicly subsidized kindergarten or private kindergarten. Children move on to primary school at six. Public primary education is free and compulsory. There are also private primary schools that cater to other groups, such as international primary schools that serve families catering to the expatriate community and families seeking an international education, as well as those who want to get prepared for studying abroad later. The samples of the current study were drawn from public kindergarten and public primary school.

@@

The city has a humid, subtropical climate and has generally mild weather. The average temperatures range from 11°C (July) to 25°C (January), but heat waves are common during the summer months (December to February).

@@

Chimfunshi wildlife orphanage is an NGO providing a home for about 150 chimpanzees. The sanctuary is located in the Copperbelt region in the northern part of Zambia close to the DRC border. The chimpanzees are housed in eight different enclosures; each of an area up to 121.5ha. The Sanctuary provides education, housing and medical care for the employees and their families which are in total about 300 people living in 5 different compounds around Chimfunshi.

@@

The Khwe (also referred to as Khoe, Khwedam, or Barakhoena) people reside in their ancestral lands within today’s Bwabwata National Park in northwestern Namibia and the bordering regions in Angola and Botswana. There is also a Khwe community in today’s South Africa that has moved there while Namibia became independent in 1990. The current research was conducted in the Namibian Zambezi region which is home to numerous small Khwe communities. There are an estimated 3 000 to 5 000 Khwe residing in Bwabwata as of today.

@@

Leipzig is a medium-sized city located in the east of Germany with a population of approximately 620 000. It serves as a significant urban center within the state of Saxony. Geographically, Leipzig is situated in the southernmost part of the North German Plain.

@@

Malatya is a big city located in the Eastern Anatolia region of Turkey with a population of approximately 800 000. Due to its strong economy based on agriculture, it is one of the biggest cities in eastern Turkey.

@@

Nyabyeya is located on a green, gently sloping area behind Nyabyeya Hill and is characterized by tropical vegetation and a savanna climate, characterized by daytime temperatures reaching 32°C/90°F and cooler nights at 17°C. The region observes two distinct agricultural seasons - a wet season from late March to June and August to November, followed by a dry season from early December to March.

@@

* Budongo Conservation Field Station: http://www.budongo.org/

* Holden, E., Buryn-Weitzel, J. C., Atim, S., Biroch, H., Donnellan, E., Graham, K. E., Hoffman, M., Jurua, M., Knapper, C. V., Lahiff, N. J., Marshall, S., Paricia, J., Tusiime, F., Wilke, C., Majid, A., & Slocombe, K. E. (2022). Maternal attitudes and behaviours differentially shape infant early life experience: A cross cultural study. PLOS ONE, 17(12), e0278378. https://doi.org/10.1371/journal.pone.0278378

@@

Ocuilan is a municipality located in the centre south of Mexico with a population of 36,223 inhabitants, distributed in 48 towns in an area of 344.84 km^2^  inside the Mexican State (Ocuilan, n.d.). Geographically Ocuilan has an altitude of between 1000 to 2 600 m situated 80 km south of Mexico City. (INEGI,2010)

@@

Plymouth is a coastal city in the South West of England with a population of more than 260 000 inhabitants. About 91% of the population was born in the UK and of those born outside of the UK, the largest proportion comes from the EU (4.5%). 95% of residents identified as White, 2.3% as Asian, and 1% as Black. English is the predominant language spoken in the city.

The city has a temperate oceanic climate with average temperatures ranging from 4 to 20°C. Winters are generally mild, and temperatures rarely drop below 0°C. Rain is frequent and highest in autumn and winter.

@@

Pune is located in the state of Maharashtra in western India. The city’s total area is 15.642 km^2^ and the municipal corporation area covers 518 km^2^. It lies on the western margin of the Deccan plateau at an altitude of 1840 feet. It is on the leeward side of the Sahyadri mountain range which forms a barrier with the Arabian Sea. The population within city limits is 4.5 million while including the metro population, it stands at 7.1 million. Pune is one of the largest information technology hubs in India and is also an important automobile and manufacturing hub. Sixty-two percent of the population in Pune is under the age of 30. The top three industries that offer employment are automotive, manufacturing and information technology and start-ups. Automobile industries such as Tata Motors, Jaguar, Renault, Volkswagen, General motors, Skoda, Force motors, Kinetic motors  and Mercedes-Benz have their manufacturing plants in Chakan, an industrial area around Pune. Cummins, a leading manufacturer of diesel and natural gas engines as well as JCB, the farm equipment company are other renowned investors. The manufacturing industry provides employment to over 600 000 people while the IT sector employs over 350 000 people. About 2.2 million migrant workers are employed in the automobile, construction and medium scale manufacturing industries.

Pune is referred to as the ‘Oxford of the East’ because of its reputed educational institutions and is also considered to be one of the most livable cities in India. The literacy rate in Pune is 86.15%.  As a result of rapid industrialization since the 1960s, a large number of people moved to Pune. Since there was inadequate housing to meet the demand, there was an increase in the number of slum dwellers. Nearly half of the slum dwellers do not have in-house toilets and 10% do not have electricity. 
Pune experiences a tropical wet and dry climate with average temperatures ranging between 20 and 28°C. Summer, monsoon and winter are the three main seasons with May being the hottest month. During summer, i.e. mid-March to mid-June, temperatures can go as high as 42°C. Monsoon lasts from June to October with most of the annual rainfall of 722mm falling between June and September with July being the wettest month. In the months of December and January, temperatures remain around 29°C with overnight temperatures dropping to below 12°C.

@@

The city is a large metropolitan area with urban and suburban areas bordered by mountain ranges to the east and west. The land is characterized by bay flats and hills with several rivers running through the city. San Jose’s climate is described as mild, semi-arid, and Mediterranean. A wet season typically occurs between November and March with combined rainfall and an average daytime temperature of 50°F. A dry season occurs between March and November where precipitation is minimal and the average daytime temperature is 70°F.

@@

Windhoek is the capital city of Namibia and is situated in the Khomas region, in the central part of the country, at an elevation of 1700 m above sea level, with a total space of 645 km^2^. The Khomas region is further divided into 10 constituencies: John Pandeni, Katutura Central, Katutura East, Khomasdal, Moses //Garoeb, Samora Machel, Tobias Hainyeko, Windhoek East, Windhoek Rural and Windhoek West. The recent 2023 census indicates that the population of the Khomas region grew by 30.8%; from 342 141 in 2011 to 494 605 in 2023.

The urban part of the Khomas region is commonly known as Windhoek, made up of the nine constituencies of the region. Windhoek rural is the rural part of the Khomas region on the outskirts of Windhoek. According to the recent 2023 census, Windhoek has a population of 486 169 (250 142 female and 236 027 male) and a population density of 94.9 persons per km^2^ (total area of 5124.2043 km^2^).

The name Windhoek is derived from the Afrikaans meaning „windy corner“. The former spelling at the beginning of the German colonial time “Windhuk” is not in use anymore. From its beginnings as a small settlement in the late 19th century, Windhoek has grown into a diverse and multi-ethnic community, home to a multitude of languages and cultures, including Nama, Owambo, Damara, Herero, Germans, Afrikaans, and British communities. Windhoek is the dominant economic and political centre of Namibia, accounting for more than 50% of the country’s manufacturing activity, over 80% of its finance and business services, and two-thirds of its community and social services. Inherited from the colonial and apartheid era, the city maintains its distinctive dual spatial structure. The city is made up of three parts: the central part consisting of the central business district (CBD); the east, south and west consisting of various suburbs housing people from primarily middle and upper socio-economic households; and the northern and north-western part of the city where more than 70% of the Windhoek population lives on 25% of the land in crowded formal and informal settlements. CBD is modern and thriving with light industrial areas to the north and south. In the center of the CBD are government offices, courts, banks, the main post office, business centers, hotels, and new modern shopping malls and supermarkets; a blend of high and low-rise modern buildings.

The current study was conducted in Cimbebasia, a suburb situated in Southern Windhoek falling within the Windhoek West constituency. According to the recent 2023 census, the total population of Windhoek West is 59 907. The household population is 56 297 with a total of 17 132 households and an average of 3.3 persons per household and a population density of 287.9 persons per km^2^ of which the area is 208.08 km^2^.

English serves as the primary medium of instruction within the educational system, but children often grow up with significant exposure to other indigenous languages like Herero and Damara within their communities. Socialization goals and parenting goals reflect that of urban communities in the Global South emphasizing “communal psychological autonomy and relatedness” (Keller & Kaertner, 2013). Children in such communities spend a significant portion of their time on activities related to school, family, and leisure with peers and siblings. Children’s exposure to smartphones, tablets, and computers begins at a relatively early age, mirroring a global trend in urban middle-class communities.

Participants came from predominantly middle-class communities and were tested at local Sunday schools (at churches) and at educational institutions.

@@

* Corbett, J. 45 Facts About Windhoek. https://facts.net/world/cities/45-facts-about-windhoek/

* Gentz, S., Chouinard, L. J., & Ruiz-Casares, M. (2022). Time use and time use satisfaction: An examination of children’s out of school activities in Namibia. Journal of the British Academy, 10s2, 59–82. https://doi.org/10.5871/jba/010s2.059

* Hamatui, N., & Beynon, C. (2017). Particulate matter and respiratory symptoms among adults living in Windhoek, Namibia: a cross sectional descriptive study. International journal of environmental research and public health, 14(2).

* Keller, H., & Kärtner, J. (2013). Development: The cultural solution of universal developmental tasks. Advances in Culture and Psychology, 3, 63–116.

* Namibia Statistics Agency. 2023 Census, Windhoek, Namibia. https://census.nsa.org.na

* Pendleton, W., & Nickanor, N. (2016). The State of Food Insecuritity in Windhoek, Namibia (No. 14). Southern African Migration Programme.
